Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-13 MS/supp.Rmd
Spelling error fixed.

Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL difference(Szymek, not sure on units, sorry)) our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_MLMA$ci.ub[1]`) is interpreted differently. Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL is `r coef(model_CS2_nuisance2)[1]` standard deviation units different. Its still a small overall effect size, but it has a clearer interpretation now. We can again calculate PI's and $I^2$ using the model. Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% -- indeed, 95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage differenc applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.

>>>>

Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL difference(Szymek, not sure on units, sorry)) our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_MLMA$ci.ub[1]`) is interpreted differently. Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL is `r coef(model_CS2_nuisance2)[1]` standard deviation units different. Its still a small overall effect size, but it has a clearer interpretation now. We can again calculate PI's and $I^2$ using the model. Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.
